% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
\usepackage{graphicx}
\usepackage[dvipsnames,usenames]{color}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document}
\name{Wang Lei\\[12pt]}   % the \\[12pt] adds a blank
        % line after name
\address{\bf  ADDRESS\\Lianzhuang Apart.\\Binjiang District\\Hangzhou,Zhejiang\\310053}
\address{\bf EMAIL\&PHONE\\E-mail: blueabysm@gmail.com\\Cellphone:  13221018836}
                                  
\begin{resume}

\textcolor{RoyalBlue}{
\section{JOB OBJECTIVE}
}
    I\rq{}m searching for a job within the software development area. I prefer to work both in C/C++ and in Web browser-side development field. I\rq{}m also quite glad to obtain some other learning opportunities.

\textcolor{RoyalBlue}{
\section{EDUCATION}
}
\vspace{-0.1in}
\begin{tabbing}
{\bf Bachelor Degree}\\
\hspace{2.3in}\= \hspace{2.6in}\= \kill
       {\it Phase}\>Sept 1, 2006 - July 1, 2010\\
       {\it Major}\>Digital Media \& Network Technology \\
       {\it College}\>College of Computer Science \& Technology \\
       {\it University}\>Zhejiang University\\
\end{tabbing}
\vspace{-20pt}

\textcolor{RoyalBlue}{
\section{COMPUTER SKILLS}
}
\vspace{-0.1in}
\begin{tabbing}
  \hspace{2.3in} \= \hspace{2.6in} \= \kill
         {\bf Familiar Languages}\>C/C++, native Javascript/Ajax/jQuery/RESTful API\\
         \>HTML, CSS, XML/XSLT/XSD\\
               {\bf Used Languages}\>PHP, C\#, JavaSE, Actionscript, Python\\
               {\bf Learning Languages}\>Ruby, Shell\\
               {\bf Database}\>MySQL\\
               {\bf Preferred Tools}\> Emacs, GDB\\
\end{tabbing}
\vspace{-20pt}          
 
\textcolor{RoyalBlue}{
\section{RECENT PUBLICATIONS}
}
\vspace{-0.1in}
\begin{tabbing}
  \hspace{2.3in} \= \hspace{2.6in} \= \kill
         {\bf Thesis Topic}\>Semantic-based Mobile Mashup Platform\\
         {\bf Published On}\>International Semantic Web Conference\\
         \>ISWC 2010 Submission 479\\
         \>Aug 23, 2010\\
               {\bf Brief}\>Mobile users could mash up the encapsulated RESTful APIs\\
               \>to produce new applications with recommendations through\\
               \>our mashup platform. Mobile mashups will contain Social\\
               \>Network Service information stored in the device, so it will\\
               \>be more meaningful to mobile users.\\
                    {\bf Related Technology}\> Javascript/XML/Ajax, Flash Lite, Python, Mobile Web Server\\
                    \end{tabbing}
\vspace{-20pt}

\textcolor{RoyalBlue}{
\section{DEVELOPMENT EXPERIENCE}
}
\vspace{-0.1in}
\begin{tabbing}
  {\bf Semantic-based Mashup}\\
  \hspace{2.3in}\= \hspace{2.6in}\= \kill
         {\it Phase}\>May 2008 - May 2009\\
         {\it Related Technologies}\>Javascript/Ajax, Silverlight, ASP.NET\\
         {\it Brief}\>Mashup is a new type of Web 2.0 application. In\\
         \>the Web 2.0 period, a huge number of websites provides\\
         \>various of RESTful APIs, e.g. Microsoft, Google,\\
         \>Yahoo! Flickr and Twitter. Mashup is a type of GUI\\
         \>application which let common users mash up the\\
         \>RESTful APIs to produce new applications easily\\
         \>without any programming. This reflects the trend of\\
         \>Web 2.0 and programmable Web.\\
         \end{tabbing}
\vspace{-20pt}

\vspace{-0.1in}
\begin{tabbing}
  {\bf Semantic-based Mobile Mashup Platform}\\
  \hspace{2.3in}\= \hspace{2.6in}\= \kill
         {\it Phase}\>Oct 2009 - May 2010\\
         {\it Related Technologies}\>Javascript/Ajax, Flash Lite, PHP, Python, Mobile Web Server etc.\\
         {\it Brief}\>Mobile users could mash up the encapsulated RESTful\\
         \>APIs to produce new applications with recommendations\\
         \>through our mashup platform. Mobile mashups will contain\\
         \>Social Network Service information, so it will be more\\
         \>meaningful to general users.\\
         \end{tabbing}
\vspace{-20pt}

\vspace{-0.1in}
\begin{tabbing}
  {\bf Other Projects}\\
  \hspace{0.3in}\= \hspace{2.6in}\= \kill
  When I’m in college, I have joined a certain amount of software projects. I\rq{}m the leader\\of the following projects:\\
  {\bf 1.}\>T-8 Photo Exchange System (Flex/Actionscript, PHP)\\
  {\bf 2.}\>TLibrary Management System (C\#, MySQL, MySQL Connector)\\
  {\bf 3.}\>Pettry 3D e-pet (C/C++, Ogre, SpeechSDK)\\
  {\bf 4.}\>Block \& Ball (C/C++). This application would have been included in the next edition\\
  \>of our mentor’s teaching materials.\\
  \end{tabbing}
\vspace{-20pt}

\textcolor{RoyalBlue}{
\section{WORK EXPERIENCE}
}
\vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill
          {\bf Requirement Analyst}\>PaxData Inc. Hangzhou\>Aug 2010 - Present\\
   \end{tabbing}
   \vspace{-20pt}
   Take the responsibilities to design the applications running on Pax POS terminals and Pax PINPads. I have finished several projects as the leader of the requirement group.
   
\textcolor{RoyalBlue}{
\section{INTERESTS}
}
\vspace{-0.1in}
\begin{tabbing}
  \hspace{2.3in}\= \hspace{2.6in}\= \kill
         {\bf Instrument \& Music}\>Sining, Keyboard, Bamboo flute\\
         {\bf Sport}\>Running\\
         {\bf Computer}\>I like playing computer tricks, and I want to be a GEEK.\\
         {\bf Others}\>Tabletop Game\\
         \end{tabbing}
\vspace{-20pt}

\textcolor{RoyalBlue}{
\section{PROFILE}
}
\vspace{-0.1in}

\begin{tabbing}
  \hspace{1.5in}\= \hspace{1.5in}\= \hspace{1.5in}\= \hspace{1.5in}\= \kill
         {\bf Name}\>Wang Lei\>{\bf Gender}\>Male\\
         {\bf Birth Date}\>July 14, 1986\>{\bf Birth Place}\>Kumul, Xinjiang\\
         {\bf Address}\>Lianzhuang Apart,\\
         \>Binjiang District,\\
         \>Hangzhou, Zhejiang\\
                   {\bf Email}\>blueabysm@gmail.com\\
                   {\bf Mobile Phone}\>13221018836\\
                   \end{tabbing}
\vspace{-20pt}

\begin{flushright}
  This resume is powered by \LaTeX\\
\end{flushright}
\end{resume}
\end{document}
